\documentclass{article}

\usepackage{html}

\begin{document}
\author{Ruey-Cheng Chen {\tt <cobain@turing.csie.ntu.edu.tw>}}
\title{Instant Refresher for {\it Effective STL}}
\date{December 27, 2010}
\maketitle

\begin{abstract}
This write-up is intensionally kept short, biased, and unorganized.
\end{abstract}

\begin{htmlonly}
  \tableofchildlinks
\end{htmlonly}

\section{Containers}

\paragraph{Choose your containers with care.}  Read the fabulous manual before
making your choice.  Containers come with subtle differences.  There is no such
thing called the default container.

\paragraph{Beware the illusion of container-independent code.} Containers are
not designed for interchangable use.  Pick one design and stick with it.

\paragraph{Make copying cheap and correct for objects in containers.} Use {\tt
vector} to prevent constructing a large number of objects
when the container is created.  Or store {\tt T*} in array instead.

\paragraph{Call {\tt empty} instead of checking {\tt size()} against zero.} For
certain containers, checking {\tt size()} is not a constant-time operation.

\paragraph{Prefer range member functions to their single-element counterparts.}
Avoid writing the loop by yourself.  Range member functions (i.e., range
constructor, {\tt insert()}, {\tt erase()}, {\tt assign()}) can be rather
straightfoward and efficient.  

\paragraph{Be alert for C++'s most vexing parse.}  Here it is:
\begin{verbatim}
  ifstream dataFile("ints.dat");
  list<int> data(istream_iterator<int>(dataFile),
                 istream_iterator<int>());
\end{verbatim}

\paragraph{When using containers of {\tt new}ed pointers, remember to {\tt
delete} the pointers before the container is destroyed.}  The container has no
right to delete these objects for you.  Write a {\tt for\_each} or use {\tt
boost::shared\_ptr} to work around.

\paragraph{Never create containers of {\tt auto\_ptr}s.}  Because 1) it can
cause problems and 2) it is prohibited in the standard.

\paragraph{Choose carefully among erasing options.} Beware iterator
invalidation when erasing elements.  Also note that the after-erase iterator
position can be a bit tricky to handle.  Here is the rule of thumbs.

\begin{itemize} \item Erase a certain value: use the erase-remove idiom, {\tt
list::remove} (if using {\tt list}), or container's {\tt erase} function.
\item Erase values that satisfy certain condition: use the erase-remove\_if idoim, {\tt
list::remove\_if}, or {\tt remove\_copy\_if} and then {\tt swap}.  \item Loop:
Update the iterator every time for sequence containers, or postincrement the
iterator for associative containers \end{itemize}

\paragraph{Be aware of allocator conventions and restrictions.}

\paragraph{Understand the legitimate uses of custom allocators.}

\paragraph{Have realistic expectations about the thread safety of STL
containers.}  Multi-read and multi-write are safe.  Otherwise, use 
{\tt boost::mutex} just to be sure.

\section{{\tt vector} and {\tt string}}

\paragraph{Prefer {\tt vector} and {\tt string} to dynamically allocated
arrays.} The title pretty much explains everything.

\paragraph{Use {\tt reserve} to avoid unnecessary reallocations.}  Think about
the algorithm that keeps a dynamic-vector growing.  This can be rather
intuitive if you expect the number of elements to be pushed into the vector go
high.

\paragraph{Be aware of variations in {\tt string} implementations.}
Different implementations returns different values for {\tt sizeof(string)}. 

\paragraph{Know how to pass {\tt vector} and {\tt string} data to legacy APIs.}
Retrieve a legacy-friendly {\tt const} string pointer by using {\tt
string::c\_str()}.  Since the internal structure of a {\tt vector} has to be
contiguous, try taking advantage of that, e.g., {\tt fillArray(\&v[0],
v.size())}.

\paragraph{Use ``the {\tt swap} trick'' to trim excess capacity.}
This is the fabulous trick:
\begin{verbatim}
  vector<Contestant> v;
  string s;
  ...
  vector<Contestant>().swap(v);
  string().swap(s);
\end{verbatim}

\paragraph{Avoid using {\tt vector<bool>}.} Because it is not an STL container
and it does not hold {\tt bool}s.

\section{Associative Containers}

\paragraph{Understand the difference between equality and equivalence.} Note
the difference between equality ({\tt operator==}) and equivalence (
{\tt operator<} or comparison functors).

\paragraph{Specify comparison types for associative containers of pointers.}
The default comparison function for {\tt std::set<T*>} is {\tt std::less<T*>},
which might not be what you want.  

\paragraph{Always have comparison functions return {\tt false} for equal
values.} Conventionally, checking for equivalence is done by evaluating {\tt
!less(a, b) \&\& !less(b, a) }.  Replacing {\tt less} with {\tt less\_equal} can
break things.

\paragraph{Avoid in-place key modification in {\tt set} and {\tt multiset}.}
Key modification can affect the element order.  Containers do not automatically
renew its structure if you do so.

\paragraph{Consider replacing associative containers with sorted {\tt
vector}s.} This is purely for efficiency.  A lot of tasks can still be done by
operating on top of a sorted {\tt vector} (e.g., {\tt binary\_search}, {\tt
nth\_element}).

\paragraph{Choose carefully between {\tt map::operator[]} and {\tt map::insert}
when efficiency is important.}  Prefer {\tt map::insert} if you only need to
insert an element.  Also check out the goodies in this item: {\tt
efficientAddOrUpdate(m, k, v)}.

\paragraph{Familiarize yourself with the nonstandard hashed containers.}
Check on {\tt std::unordered\_map} and {\tt std::unordered\_set}.

\section{Iterators}

\paragraph{Prefer {\tt iterator} to {\tt const\_iterator}, {\tt
reverse\_iterator}, and\\
{\tt const\_reverse\_iterator}.}  Stick to {\tt
iterator} if you do not have a preference.  An {\tt iterator} can be implicitly
converted to any of the others.

\paragraph{Use {\tt distance} and {\tt advance} to convert a container's {\tt
const\_iterator}s to {\tt iterator}s.}  This is how it's done.
\begin{verbatim}
  advance(i, distance<T::const_iterator>(i, ci);
\end{verbatim}

\paragraph{Understand how to use a {\tt reverse\_iterator}'s base {\tt iterator}.}

\paragraph{Consider {\tt istreambuf\_iterator}s for character-by-character input.}
Get familiar with this super-cool {\tt istream\_iterator} sibling.

\section{Algorithms}

\paragraph{Make sure destination ranges are big enough.}  Use {\tt inserter}s
to simplify the insertion into a {\tt vector}.  Calling {\tt reserve} in
advance might also be a good idea.

\paragraph{Know your sorting options.} In short, pick the right algorithm for
your task.  Here is a list of algorithms sorted in descending order of
computational efficiency: {\tt partition}, {\tt stable\_partition}, {\tt
nth\_element}, {\tt partial\_sort}, {\tt sort}, and {\tt stable\_sort}.

\paragraph{Follow {\tt remove}-like algorithms by {\tt erase} if you really
want to remove something.}  As in:
\begin{verbatim}
  vector<int> v;
  ...
  v.erase(remove(v.begin(), v.end(), 99), v.end());
\end{verbatim}

\paragraph{Be wary of {\tt remove}-like algorithms on containers of pointers.}
It might cause memory leak.  Consider nullify the pointers of interest in
advance (with a {\tt for\_each}) and then apply the {\tt remove}-{\tt erase}
idiom.

\paragraph{Note which algorithms expect sorted ranges.} Keep the STL manual in
reach.

\paragraph{Implement simple case-insensitive string comparisons via {\tt
mismatch} or {\tt lexicographical\_compare}.}  Put this down on the
corresponding manual pages for both algorithms.

\paragraph{Understand the proper implementation of {\tt copy\_if}.} Write your
own {\tt copy\_if}.

\paragraph{Use {\tt accumulate} or {\tt for\_each} to summarize ranges.} One
best thing about {\tt for\_each} is that it returns the functor.  Make it
stateful.

\section{Functors, Functor Classes, Functions, etc.}

\paragraph{Design functor classes for pass-by-value.} It means the functors
have to be small and monomorphic.  Try ``pimpl'' idiom to wrap things up.

\paragraph{Make predicates pure functions.} Because you want the predicates to
be stateless.

\paragraph{Make functor classes adaptable.} Implement the traits, or do public
inheritence from {\tt std::unary\_function} or {\tt std::binary\_function}.

\paragraph{Understand the reasons for {\tt ptr\_fun}, {\tt mem\_fun}, and {\tt
mem\_fun\_ref}.} Because they rock, dude.

\paragraph{Make sure {\tt less<T>} means {\tt operator<}.} Do not mess with
{\tt std::*}.  Do it with {\tt operator<}.

\section{Programming with the STL}

\paragraph{Prefer algorithm calls to hand-written loops.}  In STL
algorithms we trust.

\paragraph{Prefer member functions to algorithms with the same names.} They are
definitely more efficient (with regard to this particular container) than the
generic algorithms.  Otherwise, those functions wouldn't be there in the first
place.

\paragraph{Distinguish among {\tt count}, {\tt find}, {\tt binary\_search},
{\tt lower\_bound}, {\tt upper\_bound}, and {\tt equal\_range}.}  Make yourself
an STL cheatsheet so that you know what to do.

\paragraph{Consider function objects instead of functions as algorithm
parameters.} The compiler can recognize the functor and inline it for you.  And
using functors sometimes can avoid certain language pitfalls.

\paragraph{Avoid producing write-only code.}  But that's what I'm really good
at.

\paragraph{Always {\tt \#include} the proper headers.} Again, check the manual
(or grep it through the directories).

\paragraph{Learn to decipher STL-related compiler diagnostics.}
Use your force.

\paragraph{Familiarize yourself with STL-related web sites.} SGI STL, STLport,
and Boost.

\end{document}
